Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-04 paper.tex
update u nat uencrtainty

Figure \ref{fig:unat_full}| represents the cumulative natural uranium
consumption as a function of time.

>>>>

Figure \ref{fig:unat_full} represents the cumulative natural uranium
consumption as a function of time. The uncertainty on the cumulative uranium
consumption grows as expected with the time and the loading of the \glspl{LWR}.
The increase stops around year 125y with the decommissioning of the last
\glspl{LWR}.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{unat_full}
    \caption{Cumulative consumption of natural uranium as a function of time. The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:unat_full}
\end{figure}

The fluctuation of the full relative uncertainty at low time are because of the
sensitivity to the fuel loading: all reactors at the beginning have synchronised
cycle, this phenomenon disappear with the gradual decommissioning of the initial
reactor, spread on 50 years.

\begin{figure}[h!!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{unat_uncer}
    \caption{Cumulative natural uranium consumption relative uncertainty, with
    in black the total uncertainty at 1$\sigma$, and in color the uncertainty
    contribution of each parameter: cooling time (blue), fuel enrichment (red),
    cycle time (green), thermal power(brown), separation efficiency (light
    blue).}\label{fig:unatr_uncer}
\end{figure}
The relative uncertainty of the total uranium consumption starts at about
$5.5\%$ a slowly drops and stabilise around $3\%$.

As expected, cooling time, separation efficiency and thermal power does
not affect the natural uranium consumption.
The uncertainty on the natural uranium consumption is dominated by the
\glspl{LWR} cycle length: shorter the cycle length is, the more fuel will be
loaded.

As the number of deployed \glspl{LWR} reactors increases, as each parameters is
sampled once for each facilities, the average length of the cycle (as well as
the number of loaded batches) converges to the reference value.
The fuel enrichment and the tail assay contribution follow a smoother behavior,
so as the total relative uncertainty decrease, their contribution increases over
time.
